Trends in the contribution of major causes of death to the black-white life expectancy gap

### 2017-06-06 Manuscript/Appendix-agestd-mort-rates.Rmd

```{r load_libraries, echo=FALSE, warning=F, message=F}
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
library(plotly)
library(forcats)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")

mortality.rates <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_combined.csv")
mortality.rates.diff <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_combined.csv")

>>>>

```{r load_libraries, echo=FALSE, warning=F, message=F}
library(dplyr)
library(purrr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
library(plotly)
library(forcats)
source("./Code/life_expectancy_functions.R")

mortality.rates <- read.csv("./Results/mortality_rates_combined.csv")
mortality.rates.diff <- read.csv("./Results/mortality_rates_diff_combined.csv")

### 2017-06-06 Manuscript/Manuscript_COD_Trends.Rmd

source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

```{r load_data, echo=F}
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))

age_cod_results_infants_AOC <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_infants_AOC.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map(age_cod_results_infants_AOC, "state", "stabbrs")

>>>>

source("./Code/life_expectancy_functions.R")
```

```{r load_data, echo=F}
BlackWhite_results <- read.csv("./Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("./Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))

age_cod_results_infants_AOC <- read.csv("./Results2/age_cod_results_infants_AOC.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map(age_cod_results_infants_AOC, "state", "stabbrs")

### 2017-06-06 Manuscript/Manuscript_COD_Trends_PNAS.Rmd

source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

```{r load_data, echo=F}
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map2(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map2(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))

age_cod_results_infants_AOC <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_infants_AOC.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map2(age_cod_results_infants_AOC, "state", "stabbrs")

>>>>

source("./Code/life_expectancy_functions.R")
```

```{r load_data, echo=F}
BlackWhite_results <- read.csv("./Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map2(BlackWhite_results, "state", "stabbrs")
cod_decomp_results <- read.csv("./Results2/cod_decomp_results.csv")
cod_decomp_results <- reorder.as.map2(cod_decomp_results, "state", "stabbrs")
cod_decomp_results$COD_rev <- factor(cod_decomp_results$COD, levels = c("Cardiovascular", "Cancers", "All other causes",
                                                                        "Communicable", "Non-communicable",  "Injuries"))

age_cod_results_infants_AOC <- read.csv("./Results2/age_cod_results_infants_AOC.csv")
age_cod_results_infants_AOC$stabbrs <- state.abb[match(age_cod_results_infants_AOC$state, state.name)]
age_cod_results_infants_AOC$stabbrs[age_cod_results_infants_AOC$state == "Washington DC"] <- "DC"
age_cod_results_infants_AOC <- reorder.as.map2(age_cod_results_infants_AOC, "state", "stabbrs")

### 2017-06-06 Manuscript/Manuscript_COD_decomp.Rmd

```{r initialize, echo=FALSE, warning=F, message=F}
library(shiny)
library(plotly)
library(viridis)
library(scales)
library(shinythemes)
library(dplyr)
library(purrr)
library(stringr)
library(DT)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

```{r read_data, echo=F}
age_cod_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results.csv")
age_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
cod_change_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_results.csv")
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")

@@

![Difference in life expectancy between black and white males, United States, 1969-2013.](/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Manuscript/export.graph.Men.bmp)

@@

![Difference in life expectancy between black and white females, United States, 1969-2013.](/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Manuscript/export.graph.Women.bmp)

>>>>

```{r initialize, echo=FALSE, warning=F, message=F}
library(shiny)
library(plotly)
library(viridis)
library(scales)
library(shinythemes)
library(dplyr)
library(purrr)
library(stringr)
library(DT)
source("./Code/life_expectancy_functions.R")
```

```{r read_data, echo=F}
age_cod_results <- read.csv("./Results/age_cod_results.csv")
age_decomp_results <- read.csv("./Results/age_decomp_results.csv")
cod_decomp_results <- read.csv("./Results/cod_decomp_results.csv")
cod_change_results <- read.csv("./Results/cod_change_results.csv")
BlackWhite_results <- read.csv("./Results/BlackWhite_results.csv")

@@

![Difference in life expectancy between black and white males, United States, 1969-2013.](./Manuscript/export.graph.Men.bmp)

@@

![Difference in life expectancy between black and white females, United States, 1969-2013.](./Manuscript/export.graph.Women.bmp)

### 2017-06-06 conferences/Max_planck_submission.Rmd

```{r initialize, echo=FALSE, warning=F, message=F}
library(plotly)
library(scales)
library(dplyr)
library(purrr)
library(stringr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

```{r read_data, echo=F}
age_cod_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results.csv")
age_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
cod_decomp_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")

>>>>

```{r initialize, echo=FALSE, warning=F, message=F}
library(plotly)
library(scales)
library(dplyr)
library(purrr)
library(stringr)
library(ggplot2)
library(stringr)
library(reshape2)
library(grid)
library(gridExtra)
source("./Code/life_expectancy_functions.R")
```

```{r read_data, echo=F}
age_cod_results <- read.csv("./Results/age_cod_results.csv")
age_decomp_results <- read.csv("./Results/age_decomp_results.csv")
cod_decomp_results <- read.csv("./Results/cod_decomp_results.csv")
BlackWhite_results <- read.csv("./Results/BlackWhite_results.csv")

### 2017-06-06 conferences/Riddell_presentation_max_planck.Rmd

source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
BlackWhite_results <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map2(BlackWhite_results, "state", "stabbrs")

@@

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```

@@

```{r, echo = F, out.width = 500}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Harper_HA_title.png")
```

```{r, echo=F, out.width = 750}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Harper_HA_fig1.png")
```

@@

```{r, echo = F, out.width = 250}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Harper_HA_quote.png")
```

@@

```{r, echo = F, out.width = 400}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/alabama.data.ex.png")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex1.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex2.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/app_ex3.gif")
```

@@

##CVD in men
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/CVD_men.png")
```

##Cancer in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Cancer_women.png")
```

##Injury in women
```{r, echo = F, out.width = 675}
include_graphics(path = "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/Injury_women.png")
```

@@

##Tennessee
```{r, echo = F, out.height = 600, out.width = 800}
age_cod_results_female <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")

age_cod_results_male <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_male.csv")

>>>>

source("./Code/life_expectancy_functions.R")
BlackWhite_results <- read.csv("./Results2/BlackWhite_results.csv")
BlackWhite_results <- reorder.as.map2(BlackWhite_results, "state", "stabbrs")

@@

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("./conferences/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("./conferences/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("./conferences/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```

@@

```{r, echo = F, out.width = 500}
include_graphics(path = "./conferences/images/Harper_HA_title.png")
```

```{r, echo=F, out.width = 750}
include_graphics(path = "./conferences/images/Harper_HA_fig1.png")
```

@@

```{r, echo = F, out.width = 250}
include_graphics(path = "./conferences/images/Harper_HA_quote.png")
```

@@

```{r, echo = F, out.width = 400}
include_graphics(path = "./conferences/images/alabama.data.ex.png")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "./conferences/images/app_ex1.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "./conferences/images/app_ex2.gif")
```

@@

```{r, echo = F, out.width = 800}
include_graphics(path = "./conferences/images/app_ex3.gif")
```

@@

##CVD in men
```{r, echo = F, out.width = 675}
include_graphics(path = "./conferences/images/CVD_men.png")
```

##Cancer in women
```{r, echo = F, out.width = 675}
include_graphics(path = "./conferences/images/Cancer_women.png")
```

##Injury in women
```{r, echo = F, out.width = 675}
include_graphics(path = "./conferences/images/Injury_women.png")
```

@@

##Tennessee
```{r, echo = F, out.height = 600, out.width = 800}
age_cod_results_female <- read.csv("./Results2/age_cod_results_female.csv")

age_cod_results_male <- read.csv("./Results2/age_cod_results_male.csv")
